---
title: "The Evolution of the Esports Industry"
author: "Mivelaz, Allan & van Kampen, Adrian"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
    toc: true
    toc_float: true
    number_sections: true
    runtime: shiny
---

# Introduction

## Overview and Motivation
The video game industry has been growing since the beginning of the millennium. From the basement of teenagers' and geeks, it has become a wide-spread industry, with multi-million dollar games being released every year.

Similarly, so-called "E-sports" have also grown, from underground friendly tournaments to international competitions that attract millions of viewers, online and in large arenas, and pay off prizes ranging to many millions of dollars to the winner teams. As with traditional sports, this popularity is also a major business opportunity for brands that wish to get visibility to a wide audience. Starting with gaming- and electronics-related brands such as peripherals manufacturers and software developers, the virtual billboards are more and more populated by major *external* brands such as beverages, clothing and many more sectors, who begin to understand that this industry is truly booming.

In this projects, we want to give some insights about the major trends in the e-sports and gaming industry which, to the uninitiated, can seem daunting, with many different games being broadcasted, tight-knit communities having their own codes, and often unusual and innovative business models adopted by teams and individual professional players.

## Related Work
- [TwitchTracker](https://www.twitchtracker.com) offer a few audience and user's statistics about [Twitch.tv](https://www.twitch.tv), one of the major video-games' streaming platform, which we wanted to recreate by our own means.
- [Kaggle](https://www.kaggle.com/) has a few nice data-sets about e-sports that use [EsportsEarnings.com](http://www.esportsearnings.com) as a source.
- [Esportsobserver.com](https://esportsobserver.com) and [McKinsey](https://www.mckinsey.com/business-functions/marketing-and-sales/our-insights/e-sports-and-the-next-frontier-of-brand-sponsorships#) also regularly publish articles about the marketing's potential of E-sports.

Since finding data about private investments are hardly possible to get for free (even following our numerous direct inquiries to parties of interest), we are limiting our analysis to freely available data.

## Initial Questions
- Showing the growing popularity of the platform [Twitch.tv](https://www.twitch.tv).
- Identify rising games/teams for potential marketing visibility.
- Compare the income of top companies in a period to see the potential of the industry.
- Determine the factors that influence the amount of money invested.
- Put all this information together to see the long term orientation of the industry.

```{r child = '01_esports_earnings.Rmd'}
```

```{r child = '02_twitch.Rmd'}
```

```{r child = '03_NewZoo.Rmd'}
```

# Conclusion

As we have seen throughout this project, the e-sports and gaming market seems to be a growing one. Tournaments are being organized with ever-growing prize pools that reflect the active communities and developers. As well as a growing market, it is a diversified one also, with many potential segments in which to enter that can reach many different niches.

Although often seen as a *teenage boys'* interest, the people that grew up playing and watching games are getting older, and more wealthy while the younger audience builds its identities around newer games. Indeed, despite the growing number of streaming platforms that compete with Twitch.tv - the first popular streaming platform - the latter still shows impressive growth rates, and gives no signs of losing momentum. It is also important to note that behind every streamer is not a single, but multiple sponsors and marketing opportunities. Unfortunately, the data to find exactly who to sponsor is hard to come by, and such decision must rely on viewers' experience and inside knowledge of the market.

It is also interesting to note that most investments in this market are concentrated mostly in Eastern Asia, and for a part in Northern America. Young generations in these countries are growing up more and more with e-sports as a primary source of entertainment, and with major computer games companies located in these areas (South Korea and Japan mostly), it is not that surprising.

Finally, although our data from investment types is not sufficient to give meaningful insights, it does show that the amount of money involved in this market is not trivial, and that it is growing.

In summary, our project aimed at giving insights into the world of gaming and e-sports, as it can often seem eclectic and uninteresting to outsiders. Despite aspects often amusing and cartoonesque of computer games, e-sports and the industry that surrounds it is becoming a major source of entertainment for ever more diverse communities, and can be taken seriously as a business opportunity, just as conventional sports have long been seen as massive goldmines for companies to advertize themselves through events such as the SuperBowl or the Soccer World Cup.