---
title: "The Evolution of the Esports Industry"
author: "Mivelaz, Allan & van Kampen, Adrian"
date: ""
runtime: shiny
output: slidy_presentation
css: style.css
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source(file = here::here("scripts/setup.R"))
```

## Our goals

- Identify potentially interesting areas of the E-sports ecosystem (games, tournaments, etc.)
- Show the popularity of streaming platforms
- Determine factors that influence gaming's popularity

## Data Sources

- [EsportsEarnings.com](http://www.esportsearnings.com)
- [TwitchTracker.com](https://www.twitchtracker.com)
- [Newzoo.com](https://platform.newzoo.com/explorer)

## E-sports earnings

```{r EE_data_import, include=FALSE}
source(file = here::here("scripts/Esport_earnings.R"))

top_plots <- list("NbTourn" = rankg_by_tournnb,
                  "Prizes" = rankg_by_prizes,
                  "PlayerNb" = rankg_by_playernb)

```

```{r game_ranks}
inputPanel(
  radioButtons(
    inputId = "EE_top_stats",
    label = "Top 5%",
    inline = TRUE,
    choices = c("Number of Tournaments", "Prizes", "Player numbers"),
    width = "100%"
  )
)


renderPlotly({

  if(input$EE_top_stats == "Number of Tournaments") {
    rankg_by_tournnb
  } else if(input$EE_top_stats == "Prizes") {
    rankg_by_prizes
  } else if(input$EE_top_stats == "Player numbers") {
    rankg_by_playernb
  }
})
```

## Twitch overview

```{r Twitch_data_import, include=FALSE}
source(file = here::here("scripts/Twitch_EDA.R"))

top_plots4 <- list("view" = aaaa,
                  "channel" = b,
                  "watched" = c,
                  "active" = d,
                  "streamed" = e,
                  "ratio" = f)
```

```{r}
inputPanel(
  radioButtons(
    inputId = "Statistics",
    label = "Statistics over time",
    inline = TRUE,
    choices = c("view", "channel", "watched", "active", "streamed"),
    width = "100%"
  )
)


renderPlotly({

  if(input$Statistics == "view") {
    aaaa
  } else if(input$Statistics == "channel") {
    b
  } else if(input$Statistics == "watched") {
    c
  } else if(input$Statistics == "active") {
    d
  } else if(input$Statistics == "streamed") {
    e
  }
})
```

## Ratio between watched and streamed

```{r}
plot_ly(data = TwitchData, x = ~TwitchData$Date, y = ~TwitchData$Hours_watched
        ,type = "scatter", mode = "lines", width = 800
        ,name = "Hours watched", height = 600) %>%
  add_trace(x = ~TwitchData$Date, y = ~TwitchData$Hours_streamed, yaxis = "y2", name = "Hours streamed") %>%
  add_trace(x = ~TwitchData$Date, y = ~TwitchData$Viewers_per_streamer, yaxis = "y3", name = "Viewers per steamers")%>%
  layout(
    yaxis = list(
      showline = FALSE, side = "left"
      ,title = ""
      , color = "blue"
    )
    ,yaxis2 = list(
      showline = FALSE
      ,overlaying = "y"
      ,title = ""
      , anchor = "free"
      , color = "orange"
    )
    ,yaxis3 = list(
      showline = FALSE,
      side = "right",
      overlaying = "y"
      ,title = ""
      , color = "green"
    )
    ,xaxis = list(
      showline = FALSE, zeroline = FALSE, dtick = 0, title = "Date"
    )
    ,showlegend = TRUE
    ,margin = list(
      pad = 30, b = 90, l = 150, r = 90
    )
    ,legend = list(orientation = "v")
    , title = "Comparaison between watched and streamed"
  )
```

## Companies revenues

```{r, include=FALSE}
source(file = here::here("scripts/NewZoo_EDA.R"))

top_plots2 <- list("2019" = aaa,
                  "2020" = bbb,
                  "YoY" = plot)

top_plots3 <- list("number" = aa,
                  "type" = bb,
                  "sector" = cc,
                  "mean" = dd)
```

```{r}
inputPanel(
  radioButtons(
    inputId = "Revenue",
    label = "Income per company",
    inline = TRUE,
    choices = c("2019", "2020", "YoY"),
    width = "100%"
  )
)


renderPlotly({

  if(input$Revenue == "2019") {
    aaa
  } else if(input$Revenue == "2020") {
    bbb
  } else if(input$Revenue == "YoY") {
    plot
  }
})
```

## Information about investment

```{r}
inputPanel(
  radioButtons(
    inputId = "Investment",
    label = "Several investment",
    inline = TRUE,
    choices = c("number", "type", "sector", "mean"),
    width = "100%"
  )
)


renderPlotly({

  if(input$Investment == "number") {
    aa
  } else if(input$Investment == "type") {
    bb
  } else if(input$Investment == "sector") {
    cc
  } else if(input$Investment == "mean") {
    dd
  }
})
```

## Conclusion

<div class='left' style='float:left;width:48%'>

### **Most interesting games**

- StarCraft II
- League of Legends
- Dota 2
- Counter-Strike: Global Offensive
- Fortnite
- Super Smash Bros. Melee</div>
<div class='right' style='float:right;width:48%'>

### **Twitch**

- popularity is growing
- corona's impact

### **NewZoo**

- Money involved is growing
- Concentrated industry</div>



