## Esports Earnings
### Data gathering

```{r, echo = FALSE, message = FALSE, include=FALSE}
source(here::here("scripts/setup.R"))
```

We accessed data about Esports Earnings through tournaments on the website [EsportsEarnings.com](http://www.esportsearnings.com) (which we abbreviate by "EE").

This website provides a rather complete API to gather data in convenient `.csv` files, through multiple *methods*. Due to website limitations (and to prevent excessive traffic on their side), we are only able to get a dataset (max. 100 rows) every second at most.

Therefore, we wrote a function `build_df()` that automates the process of making API requests and builds complete datasets, 100 rows at a time, for several different methods. This function can be found in the "scripts/Functions.R" script.

Using this, we gathered several datasets:

--------------------


```{r}
tournaments <- read_csv(file = here::here("data/EsportsEarnings.com/EE_tournaments.csv"))

tournaments %>% kable_head(caption = "Registered e-sports tournaments since 1996")
```

<p>&nbsp;</p>

`EE_tournaments.csv` contains most registered esports tournaments across various computer games. The dataset contains 41,213 observations of 9 variables. For the not so self-explanatory variables:
- **GameId** corresponds to the game being played.
- **Teamplay** is 1 if the game if entities competing are teams, and 0 if the tournament is individual.

--------------------------------

```{r}
teams <- read_csv(file = here::here("data/EsportsEarnings.com/EE_teams_earnings.csv"))

teams %>% kable_head(caption = "Teams' total earnings")
```

<p>&nbsp;</p>

`EE_teams_earnings.csv` contains most registered teams' earnings throughout their history. It contains observations about 1,213 teams.

--------------------------------

```{r}
games <- read_csv(file = here::here("data/EsportsEarnings.com/EE_games_earnings.csv")) %>%
  rename(GameId = id) # We add this to harmonize variables name across datasets

games %>% kable_head(caption = "Prize money gained in each game.")
```

<p>&nbsp;</p>

`EE_games_earnings.csv` contains all the prize money won across most registered tournaments throughout each game's history. The dataset contains observations about 480 different games.

---------------------------------

## Initial EDA
### Ranking different games

Using the `EE_games_earnings.csv`, we displayed a few statistics to see the top games in each one (displaying only the top 5% for each statistic).

```{r}
o_prizes <- games %>%
  select(GameId, GameName, TotalUSDPrize) %>%
  filter(TotalUSDPrize > quantile(TotalUSDPrize, p=0.95, na.rm=TRUE)) %>%
  arrange(desc(TotalUSDPrize))

o_prizes %>%
  ggplot(aes(x=reorder(GameName, TotalUSDPrize), y=TotalUSDPrize/1000000)) +
  geom_bar(stat="sum", show.legend = FALSE) +
  scale_y_continuous(labels = comma) +
  ylab("Total Prizes (in mio of USD)") +
  xlab("") +
  coord_flip()
```

<p>&nbsp;</p>

-----------------------------------------

```{r}
o_tourn <- games %>%
  select(GameId, GameName, TotalTournaments) %>%
  arrange(desc(TotalTournaments)) %>%
  filter(TotalTournaments > quantile(TotalTournaments, p=0.95, na.rm=TRUE))

o_tourn %>%
  ggplot(aes(x=reorder(GameName, TotalTournaments), y=TotalTournaments)) +
  geom_bar(stat="sum", show.legend = FALSE) +
  xlab("") +
  ylab("Number of tournaments") +
  coord_flip()
```

<p>&nbsp;</p>

-----------------------------------

```{r}
o_players <- games %>%
  select(GameId, GameName, TotalPlayers) %>%
  arrange(desc(TotalPlayers)) %>%
  filter(TotalPlayers > quantile(TotalPlayers, p=0.95, na.rm=TRUE))

o_players %>%
  ggplot(aes(x=reorder(GameName, TotalPlayers), y=TotalPlayers)) +
  geom_bar(stat="sum", show.legend = FALSE) +
  xlab("") +
  ylab("Number of professional players") +
  coord_flip()
```

<p>&nbsp;</p>
--------------------

### Evolution of Esports Tournaments

We display some statistics about the evolution of esports, starting with the number of tournaments organized each month (since the first recorded tournament in 1996):

```{r}
tournaments1 <- tournaments %>%
  left_join(games, by = "GameId") %>%
  rename(TotalUSDPrize = TotalUSDPrize.x, X = X1.x) %>%
  select(X:GameId,
         GameName,
         TournamentName:TotalUSDPrize) %>%
  mutate(StartDate = as_date(StartDate), EndDate = as_date(EndDate))

monthly_tourn <- tournaments1 %>%
  group_by(Month_Yr = floor_date(EndDate, "month")) %>%
  summarize(number = n(),
            totalPrize = sum(TotalUSDPrize))

tourn_nb <- monthly_tourn %>% ggplot(aes(x = Month_Yr)) +
  geom_line(aes(y=number)) +
  ylab("Number of tournaments per month") +
  xlab("Month")

tourn_nb
```

<p>&nbsp;</p>

We can also display the monthly total prize money won in these tournaments:

```{r}
tourn_money <- monthly_tourn %>% 
  ggplot(aes(x = Month_Yr, y=totalPrize)) +
  geom_col() +
  ylab("Total prizes won") +
  xlab("Month")

tourn_money
```

<p>&nbsp;</p>
-------------------
### Teams statistics

Teams with highest earnings:

```{r}
o_teams <- teams %>%
  arrange(desc(TotalUSDPrize)) %>%
  filter(X1 < 21, na.rm = TRUE)

o_teams %>%
  ggplot(aes(x=reorder(TeamName, TotalUSDPrize), y=TotalUSDPrize/1000000)) +
  geom_col() +
  xlab("") +
  ylab("Total USD Prize (in mio USD)") +
  coord_flip()
```

<p>&nbsp;</p>

Teams with most tournaments played:

```{r}
o_teams <- teams %>%
  arrange(desc(TotalTournaments)) %>%
  filter(X1 < 21, na.rm = TRUE)

o_teams %>%
  ggplot(aes(x=reorder(TeamName, TotalTournaments), y=TotalTournaments)) +
  geom_col() +
  xlab("") +
  ylab("Total tournaments played") +
  coord_flip()
```

<p>&nbsp;</p>


## Tournaments by game

We would like to learn a bit more about the life-cycle of games in the competitive arena. For that, let's observe the frequency of tournaments for different games:

```{r}
facetnb <- 4

tourn_bygame <- tournaments1 %>%
  filter(GameId %in% o_tourn$GameId[1:facetnb]) %>%
  group_by(Month_Yr = floor_date(EndDate, "month"), GameId) %>%
  summarize(number= n())

game_ev_tourn <- tourn_bygame %>%
  ggplot(aes(x=Month_Yr, y=number)) +
  geom_line() +
  xlab("") +
  ylab("Tournaments per month") +
  facet_wrap(tourn_bygame$GameId)

game_ev_tourn
```
----------------------