## Esports Earnings
### Data gathering

```{r, echo = FALSE, message = FALSE, include=FALSE}
source(here::here("scripts/setup.R"))
```

We accessed data about Esports Earnings through tournaments on the website <www.esportsearnings.com> (which we abbreviate by "EE").

This website provides a rather complete API to gather data in convenient *.csv* files, through multiple *methods*. Due to website limitations (and to prevent excessive traffic on their side), we are only able to get a dataset (max. 100 rows) every second at most.

Therefore, we built a **build_df** function that automates the process of making API requests and builds complete datasets, 100 rows at a time, for several different methods. This function can be found in the "scripts/Functions.R" script.

Using this, we gathered several datasets:


```{r}
tournaments <- read_csv(file = here::here("data/EsportsEarnings.com/EE_tournaments.csv"))

tournaments %>% kable_head(caption = "EE_tournaments.csv contains most registered e-sports tournaments since 1996")
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
