# EDA for Newzoo data-set

## These data comes from the website : [Newzoo](https://platform.newzoo.com/explorer)

```{r, echo=FALSE, warning=FALSE, message=FALSE}
source(here::here("scripts/setup.R"))
```

```{r}
data2 <- read_delim(file = here::here("data/NZ_CompaniesPublicRevenues2.csv"), ";", escape_double = FALSE, col_names = FALSE, trim_ws = TRUE)
```

```{r}
# Data cleaning

CompaniesPublicRevenues <- data2 %>%
   # set a name for each variable
   rename(Company_name = X1, Region_of_HQ = X2, Q1_2019 = X3, 
          Q2_2019 = X4, Q3_2019 = X5, Q4_2019 = X6, 
          Q1_2020 = X7, Q2_2020 = X8) %>%
   # modify the format of certain variable   
   mutate(Q1_2019 = parse_number(Q1_2019), Q2_2019 = parse_number(Q2_2019),
          Q3_2019 = parse_number(Q3_2019), Q4_2019 = parse_number(Q4_2019),
          Q1_2020 = parse_number(Q1_2020), Q2_2020 = parse_number(Q2_2020)) %>%
   # put every variable in the same unit
   mutate(Q1_2019 = ifelse(Q1_2019 < 10 , Q1_2019*1000, Q1_2019), 
          Q2_2019 = ifelse(Q2_2019 < 10 , Q2_2019*1000, Q2_2019), 
          Q3_2019 = ifelse(Q3_2019 < 10 , Q3_2019*1000, Q3_2019), 
          Q4_2019 = ifelse(Q4_2019 < 10 , Q4_2019*1000, Q4_2019),
          Q1_2020 = ifelse(Q1_2020 < 10 , Q1_2020*1000, Q1_2020),
          Q2_2020 = ifelse(Q2_2020 < 10 , Q2_2020*1000, Q2_2020)) %>%
   # compute total and growth
  mutate(First_semester_of_2019 = Q1_2019 + Q2_2020, 
         Second_semester_of_2019 = Q3_2019 + Q4_2019, 
         Total_in_2019 = Q1_2019 + Q2_2019 + Q3_2019 + Q4_2019, 
         First_semester_in_2020 = Q1_2020 + Q2_2020) %>%
  mutate(Q1_grate = 100*(Q1_2020 - Q1_2019)/Q1_2019, 
         Q2_grate = 100*(Q2_2020 - Q2_2019)/Q2_2019, 
         Semester2_grate = 100*(Second_semester_of_2019 - First_semester_of_2019)/First_semester_of_2019,
         Semester3_grate = 100*(First_semester_in_2020 - Second_semester_of_2019)/Second_semester_of_2019,
         First_semester_grate = 100*(First_semester_in_2020 - First_semester_of_2019)/First_semester_of_2019)

# Data overview 

CompaniesPublicRevenues %>% 
   kbl(caption = "Game revenu per company") %>%
   kable_paper(full_width = F) %>% 
   add_header_above(c(" " = 2, "2019" = 4, "2020" = 2, "Total per semester/year" = 4, "Growth rate" = 5)) %>%
   scroll_box(width = "100%", height = "300px")
```

<p>&nbsp;</p>
`CompaniesPublicRevenues.csv` contains the revenue of the top 25 game companies for several period, where `Q1`, `Q2`, `Q3` and `Q4` correspond to every quarter of the year. For example, we can see which company generated most income in 2019.

```{r}
o_total_in_2019 <- CompaniesPublicRevenues %>%
   ggplot(aes(x = reorder(Company_name, Total_in_2019), y = Total_in_2019)) +
   geom_col() +
   xlab("Company name") +
   ylab("Total game revenue in 2019") +
   coord_flip()
o_total_in_2019
```

### Here an other dataset about the amount of different investment
<p>&nbsp;</p>

```{r}
data3 <- read_delim(file = here::here("data/NZ_CompaniesInvestmentscsv1.csv"), ";", escape_double = FALSE, col_names = FALSE, trim_ws = TRUE)

data4 <- read_delim(file = here::here("data/NZ_CompaniesInvestmentscsv2.csv"), ";", escape_double = FALSE, col_names = FALSE, trim_ws = TRUE)

CompaniesInvestments <- data3 %>% full_join(data4) %>%
  rename(Date = X1, "Investment type" = X2, Sectors = X3, Emptycolumn = X4, Investee = X5, Amount = X6) %>%
  mutate(Date = dmy(Date), Emptycolumn = NULL, Sectors = str_replace_all(Sectors, ",.", ", "))


CompaniesInvestments %>% 
   kbl(caption = "Twitch statistics") %>%  
   kable_paper(full_width = F) %>% 
   scroll_box(width = "100%", height = "300px")
```

<p>&nbsp;</p>
`CompaniesInvestment.csv` contains the amount of several investment. It will be usefull to see if the amount is growing over the years and if depends on several factor such as the `Sectors` or the `Investment type`.