# EDA for Newzoo data-set

## These data comes from the website : [Newzoo](https://platform.newzoo.com/explorer)

```{r, echo=FALSE, warning=FALSE, message=FALSE}
source(here::here("scripts/setup.R"))
```

```{r}
# Load the data

data1 <- read_delim(file = here::here("data/NZ_CompaniesPublicRevenues2.csv"), ";", escape_double = FALSE, col_names = FALSE, trim_ws = TRUE)
```

```{r}
# Data cleaning

CompaniesPublicRevenues <- data1 %>%
  # set a name for each variable
  rename(Company_name = X1, Region_of_HQ = X2, Q1 = X3, 
         Q2 = X4, Q3 = X5, Q4 = X6, 
         Q1_2020 = X7, Q2_2020 = X8) %>%
  # modify the format of certain variable   
  mutate(Q1 = parse_number(Q1), Q2 = parse_number(Q2),
         Q3 = parse_number(Q3), Q4 = parse_number(Q4),
         Q1_2020 = parse_number(Q1_2020), Q2_2020 = parse_number(Q2_2020)) %>%
  # put every variable in the same unit
  mutate(Q1 = ifelse(Q1 < 10 , Q1*1000, Q1), 
         Q2 = ifelse(Q2 < 10 , Q2*1000, Q2), 
         Q3 = ifelse(Q3 < 10 , Q3*1000, Q3), 
         Q4 = ifelse(Q4 < 10 , Q4*1000, Q4),
         Q1_2020 = ifelse(Q1_2020 < 10 , Q1_2020*1000, Q1_2020),
         Q2_2020 = ifelse(Q2_2020 < 10 , Q2_2020*1000, Q2_2020)) %>%
  # compute total and growth
  mutate(Total_2019 = Q1 + Q2 + Q3 + Q4, .after = Q4) %>%
  mutate(Total_2020 = Q1_2020 + Q2_2020, .after = Q2_2020) %>%
  mutate(Q1_grate = 100*(Q1_2020 - Q1)/Q1, .after = Q1_2020) %>% 
  mutate(Q2_grate = 100*(Q2_2020 - Q2)/Q2, .after = Q2_2020)

# ------------------------------------------------------------------------------

# Data overview 

CompaniesPublicRevenues %>%
  rename("Q1 " = Q1_2020, "Q2 " = Q2_2020, "Full year" = Total_2019, 
         "YoY growth for Q1 (%)" = Q1_grate,"Half year " = Total_2020, 
         "YoY growth for Q2 (%) " = Q2_grate) %>%
  kbl(caption = "Game revenu per company") %>%
  kable_paper(full_width = F) %>% 
  add_header_above(c(" " = 2, "2019" = 5, "2020" = 5)) %>%
  scroll_box(width = "100%", height = "300px")
```

<p>&nbsp;</p>
`CompaniesPublicRevenues.csv` contains the revenue of the top 25 game companies for several period, where `Q1`, `Q2`, `Q3` and `Q4` correspond to every quarter of the year. For example, we can see which company generated most income in 2019.

```{r}
o_total_in_2019 <- CompaniesPublicRevenues %>%
   ggplot(aes(x = reorder(Company_name, Total_2019), y = Total_2019)) +
   geom_col() +
   xlab("Company name") +
   ylab("Total game revenue in 2019") +
   coord_flip()
o_total_in_2019
```

### Here an other dataset about the amount of different investment
<p>&nbsp;</p>

```{r}
# Load the data

data3 <- read_delim(file = here::here("data/NZ_CompaniesInvestmentscsv1.csv"), 
                    ";", escape_double = FALSE, col_names = FALSE, trim_ws = TRUE)

data4 <- read_delim(file = here::here("data/NZ_CompaniesInvestmentscsv2.csv"), 
                    ";", escape_double = FALSE, col_names = FALSE, trim_ws = TRUE)
```

```{r}
# Data cleaning

CompaniesInvestments <- data3 %>%
  # combine the 2 data-sets
  full_join(data4) %>%
  # set a name for each variable
  rename(Date = X1, "Investment type" = X2, Sectors = X3, Emptycolumn = X4, Investee = X5, Amount = X6) %>%
  # modify the format of certain variable
  mutate(Date = dmy(Date), Emptycolumn = NULL, Sectors = str_replace_all(Sectors, ",.", ", "))

# Data overview

CompaniesInvestments %>% 
  kbl(caption = "Ammount of different investment") %>%
  kable_paper(full_width = F) %>% 
  scroll_box(width = "100%", height = "300px")
```

<p>&nbsp;</p>
`CompaniesInvestment.csv` contains the amount of several investment. It will be usefull to see if the amount is growing over the years and if depends on several factor such as the `Sectors` or the `Investment type`.