---
title: "The evolution of the esports industry"
author: "Mivelaz, Allan and van Kampen, Adrian"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

## Overview and Motivation:
Having both an interest in competitive video-games, we have watched and followed major esports events and teams in the past. From humble independent beginnings, the sector has become a
multi-million dollar industry in a few years, with large companies (including out of the sector, such as
Louis-Vuitton) starting to sponsor teams and whole events more and more frequently, and prize-pools
for tournaments ever-increasing.
Regular sports have become saturated, with tournaments having a well-established fan base and
sponsors, but not growing very much. E-sports, on the other hand, is a rising sector with regular
growth in viewership and hence a very interesting market to invest early on from a sponsor's point-ofview.
Esports, standing for electronic sports, is a growing phenomenon. 
Our project aims to show the trends in the esports industry. To do so, we will compare some data to see how it has evolved over the past few years.

## Related Work:
Many report/data/statistics are available on our subject. Here are some link that has inspired us.
- Twitchtracker.com
- https://esportsobserver.com
- https://www.mckinsey.com/business-functions/marketing-and-sales/our-insights/e-sports-and-the-next-frontier-of-brand-sponsorships#
- kaggle.com

Although these links contain very extensive studies that we will unfortunately not be able to reproduce, we will try to do our best to show an overview of this industry.

## Initial Questions:
- Show the growing popularity of the platform Twitch 
- Identify rising games/teams for potential marketing visibility.
- Compare the income of top companies in a period to see the potential of the industry.
- Determine the factors that influence the amount of money invested 
- Put all this information together to see the long term orientation of the industry

```{r child = 'Twitch_data.Rmd'}
```

```{r child = 'New_zoo_data.Rmd'}
```

```{r child = 'esports_earnings_data1.Rmd'}
```