---
title: "An overview of the NewZoo statistics"
author: "Mivelaz Allan"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: readable
    toc: true
    toc_float: true
    number_sections: true
    runtime: shiny
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
source(here::here("scripts/setup.R"))
```

# Company public revenue

NewZoo is *"the world's go-to destination for accurate and actionable games data"*. It gives insight about several aspects in the video games industry. As part of our project, we will use it to collect data on the income and investments of certain companies. 

## Data sources and description {.tabset .tabset-fade}

These data comes from the website : [Newzoo.com](https://platform.newzoo.com/explorer)
We will start our analysis by regarding the revenue of the top 25 video company in the world. We will use this data to figure out which company generate most income and how it has evolved over the last 2 years.

### Data overview

```{r}
# Load the data

data1 <- read_delim(file = here::here("data/NZ_CompaniesPublicRevenues2.csv"), ";", escape_double = FALSE, col_names = FALSE, trim_ws = TRUE)

numeric_Q1 <- c()
for(i in seq_along(data1$X3)){
  x <- parse_number(data1$X3[i])*(10 ** (3*as.integer(regexpr(str_sub(data1$X3[i], -1 , -1), 'KMB'))))
  numeric_Q1 <- c(numeric_Q1, x)
}

numeric_Q2 <- c()
for(i in seq_along(data1$X4)){
  x <- parse_number(data1$X4[i])*(10 ** (3*as.integer(regexpr(str_sub(data1$X4[i], -1 , -1), 'KMB'))))
  numeric_Q2 <- c(numeric_Q2, x)
}

numeric_Q3 <- c()
for(i in seq_along(data1$X5)){
  x <- parse_number(data1$X5[i])*(10 ** (3*as.integer(regexpr(str_sub(data1$X5[i], -1 , -1), 'KMB'))))
  numeric_Q3 <- c(numeric_Q3, x)
}

numeric_Q4 <- c()
for(i in seq_along(data1$X6)){
  x <- parse_number(data1$X6[i])*(10 ** (3*as.integer(regexpr(str_sub(data1$X6[i], -1 , -1), 'KMB'))))
  numeric_Q4 <- c(numeric_Q4, x)
}

numeric_Q1_2020 <- c()
for(i in seq_along(data1$X7)){
  x <- parse_number(data1$X7[i])*(10 ** (3*as.integer(regexpr(str_sub(data1$X7[i], -1 , -1), 'KMB'))))
  numeric_Q1_2020 <- c(numeric_Q1_2020, x)
}

numeric_Q2_2020 <- c()
for(i in seq_along(data1$X8)){
  x <- parse_number(data1$X8[i])*(10 ** (3*as.integer(regexpr(str_sub(data1$X8[i], -1 , -1), 'KMB'))))
  numeric_Q2_2020 <- c(numeric_Q2_2020, x)
}

# Data for computation

CompRev <- data1 %>%
  # set a name for each variable
  rename(Company_name = X1, Region_of_HQ = X2, Q1 = X3, 
         Q2 = X4, Q3 = X5, Q4 = X6, 
         Q1_2020 = X7, Q2_2020 = X8) %>%
  # modify the format of certain variable   
  mutate(Q1 = numeric_Q1, Q2 = numeric_Q2,
         Q3 = numeric_Q3, Q4 = numeric_Q4,
         Q1_2020 = numeric_Q1_2020, Q2_2020 = numeric_Q2_2020) %>%
  # compute total and growth
  mutate(Total_2019 = Q1 + Q2 + Q3 + Q4, .after = Q4) %>%
  mutate(Half_2020 = Q1_2020 + Q2_2020, .after = Q2_2020) %>%
  mutate(Q1_grate = 100*(Q1_2020 - Q1)/Q1, .after = Q1_2020) %>% 
  mutate(Q2_grate = 100*(Q2_2020 - Q2)/Q2, .after = Q2_2020)

# Data for visualization

CompRev2 <- CompRev %>%
  mutate(Q1 = data1$X3, Q2 = data1$X4, Q3 = data1$X5,
         Q4 = data1$X6, Q1_2020 = data1$X5, Q2_2020 = data1$X6,
         Total_2019 = ifelse(Total_2019 >= 1000000000, 
                             f_bills(Total_2019, prefix = "$", digits = 12), 
                             f_mills(Total_2019, prefix = "$", digits = 9)),
         Half_2020 = ifelse(Half_2020 >= 1000000000, 
                            f_bills(Half_2020, prefix = "$", digits = 12), 
                            f_mills(Half_2020, prefix = "$", digits = 9)),
         Q1_grate = paste0(round(Q1_grate, digits = 2), "%"), 
         Q2_grate = paste0(round(Q2_grate, digits = 2), "%"))

# ------------------------------------------------------------------------------

# Data overview 

CompRev2 %>%
  rename("Company name" = Company_name, "Region of HQ" = Region_of_HQ,
         "Q1 " = Q1_2020, "Q2 " = Q2_2020, "Full year" = Total_2019, 
         "YoY growth" = Q1_grate,"Half year " = Half_2020, 
         "YoY growth " = Q2_grate) %>%
  kbl(caption = "Game revenu per company") %>%
  kable_paper(full_width = F) %>% 
  add_header_above(c(" " = 2, "2019" = 5, "2020" = 5)) %>%
  scroll_box(width = "100%", height = "300px")
```

<p>&nbsp;</p>

We can see that these data consist of 25 observations of 12 attributes. 

Here is a description of each attribute :
   
- `Company name` : the name of the company
- `Region of HQ` : where the company is based
- `Q1` (2019 and 2020) : January to March income 
- `Q2` (2019 and 2020) : April to June income
- `Q3` : July to September income
- `Q4` : October to December income
- `YoY` (Q1 and Q1) : give the growth for a period after 1 year
- `Full year` : give the total income in 2019
- `Half year` : give to total income for the first six months in 2020

### Summary

```{r}
# General statistics for the numeric variable

summary(CompRev[, -c(1,2)] %>% rename("Income in 2019 (Q1)" = Q1,
         "Income in 2019 (Q2)" = Q2,
         "Income in 2019 (Q3)" = Q3,
         "Income in 2019 (Q4)" = Q4,
         "Total income in 2019" = Total_2019,
         "Income in 2020 (Q1)" = Q1_2020,
         "YoY growth rate in Q1" = Q1_grate,
         "Income in 2020 (Q2)" = Q2_2020,
         "YoY growth rate in Q2" = Q2_grate,
         "Income for the first half of 2020" = Half_2020
         ))
```

<p>&nbsp;</p>

We can see here the basic statistics for every variable. They show a big gap between the min and the max, as well as between the mean and the median. We will try to determine the factors that influence these gaps.

## Exploratory Data Analysis

We can see from the table that revenues vary greatly from one business to another. To have a better view on the difference, let's represent these values on a graph.

### Income per company {.tabset .tabset-fade}

#### Total income in 2019

```{r}
plot_CompRev <- CompRev %>%
  mutate(Company_name = factor(CompRev$Company_name, 
                               levels = unique(CompRev$Company_name)[order(CompRev$Total_2019, decreasing = FALSE)]))

plot_ly(data = plot_CompRev,
        x = plot_CompRev$Total_2019,
        y = ~plot_CompRev$Company_name,
        color = ~plot_CompRev$Company_name,
        colors = "Dark2",
        type = "bar",
        height = 600) %>% 
  layout(title = "Income per company",
         xaxis = list(title = "Revenue"),
         yaxis = list(title = ""),
         showlegend = FALSE)
```

<p>&nbsp;</p>

Here, we can clearly see the gap between companies, it also explains the difference between the mean and median : the first five companies generate more than all the other together. Although the market is very competitive, it is still dominated by only a few companies. Let's have a look now on the 2020 income, to see of we have the same ranking.

#### Total income in 2020

```{r}
plot_CompRev_2020 <- CompRev %>%
  mutate(Company_name = factor(CompRev$Company_name, 
                               levels = unique(CompRev$Company_name)[order(CompRev$Total_2019, decreasing = FALSE)]))

plot_ly(data = plot_CompRev_2020,
        x = plot_CompRev_2020$Half_2020,
        y = ~plot_CompRev_2020$Company_name,
        color = ~plot_CompRev_2020$Company_name,
        colors = "Dark2",
        type = "bar",
        height = 600) %>% 
  layout(title = "Income per company",
         xaxis = list(title = "Revenue"),
         yaxis = list(title = ""),
         showlegend = FALSE)
```

<p>&nbsp;</p>

In order to see to evolution after 1 year, we have decided to keep the same order as in 2019. It is noticeable that although there is almost no change between the largest companies, for medium and small companies the competition is much tougher, with many changes in the ranking. Let's see if the YoY growth rate can explain it !

#### YoY growth rate

```{r}
YoY <- CompRev %>%
  mutate(Q1_grate = (round(Q1_grate, digits = 2)),
         Company_name = factor(CompRev$Company_name, 
                               levels = unique(CompRev$Company_name)[order(CompRev$Total_2019, decreasing = FALSE)]))

# Q1 growth rate
plot1 <- plot_ly(YoY, x = ~Q1_grate, y = ~Company_name, type = "bar", name = 'YoY growth for Q1 (%)', height = 500, width = 800) %>% 
  layout(title = "",
         xaxis = list(title = "Growth rate (%)"),
         yaxis = list(title = ""),
         showlegend = FALSE)

# Q1 growth rate
plot2 <- plot_ly(YoY, x = ~Q2_grate, y = ~Company_name, type = "bar", name = 'Yoy growth for Q2 (%)', height = 500, width = 800) %>% 
  layout(title = "",
         xaxis = list(title = "Growth rate (%)"),
         yaxis = list(title = ""),
         showlegend = FALSE)

plot <- subplot(plot1, plot2, margin = 0, shareY = TRUE, titleX = T)

plot
```

<p>&nbsp;</p>

Keeping the same ranking (by total income in 2019), we can see that having a high income does not necessarily imply a high growth rate. It is even clearer for Q1, where we can see a negative correlation. (the less revenue you have, the higher the growth rate will be)

<hr/>

### {-}

Now that we have seen the revenues of several companies, let's see if the region of the HQ can influence them.

### Mean and total income per region {.tabset .tabset-fade}

#### 2019 full year

```{r}
CompRev_HQ2019 <- CompRev %>% 
  mutate(Region_of_HQ = factor(CompRev$Region_of_HQ, 
                               levels = unique(CompRev$Region_of_HQ)[order(CompRev$Total_2019, decreasing = FALSE)])) 

plot_CompRev_HQ2019 <- CompRev_HQ2019 %>%
  group_by(Region_of_HQ) %>% 
  summarize(total = sum(Total_2019), 
            number = sum(Total_2019 > 0), 
            mean = mean(Total_2019),
            median = median(Total_2019))

plot_ly(data = plot_CompRev_HQ2019,
        x = plot_CompRev_HQ2019$Region_of_HQ,
        y = ~plot_CompRev_HQ2019$mean,
        color = ~plot_CompRev_HQ2019$Region_of_HQ,
        colors = "Dark2",
        type = "bar",
        name = "Total income",
        height = 400) %>% 
  add_trace(y = ~plot_CompRev_HQ2019$total, name = 'Mean') %>%
  layout(title = "Mean and income per Region",
         xaxis = list(title = "Revenue"),
         yaxis = list(title = ""),
         margin = list(b = 0),
         barmode = "group",
         showlegend = FALSE)
```

#### 2020 half year

```{r}
CompRev_HQ2020 <- CompRev %>% 
  mutate(Region_of_HQ = factor(CompRev$Region_of_HQ, 
                               levels = unique(CompRev$Region_of_HQ)[order(CompRev$Total_2019, decreasing = FALSE)])) 

plot_CompRev_HQ2020 <- CompRev_HQ2020 %>%
  group_by(Region_of_HQ) %>% 
  summarize(total = sum(Half_2020),
            number = sum(Half_2020 > 0), 
            mean = mean(Half_2020),
            median = median(Half_2020))

plot_ly(data = plot_CompRev_HQ2020,
        x = plot_CompRev_HQ2020$Region_of_HQ,
        y = ~plot_CompRev_HQ2020$mean,
        color = ~plot_CompRev_HQ2020$Region_of_HQ,
        colors = "Dark2",
        type = "bar",
        name = "Total income",
        height = 400) %>% 
  add_trace(y = ~plot_CompRev_HQ2020$total, name = 'Mean') %>%
  layout(title = "Mean and income per Region",
         xaxis = list(title = "Revenue"),
         yaxis = list(title = ""),
         margin = list(b = 0),
         barmode = "group",
         showlegend = FALSE)
```

#### Number of company

```{r}
plot_ly(data = plot_CompRev_HQ2020,
        x = plot_CompRev_HQ2020$Region_of_HQ,
        y = ~plot_CompRev_HQ2020$number,
        color = ~plot_CompRev_HQ2020$Region_of_HQ,
        colors = "Dark2",
        type = "bar",
        name = "Total income",
        height = 400
        ) %>%
  layout(title = "Number of company per region",
         xaxis = list(title = "Region"),
         yaxis = list(title = ""),
         showlegend = FALSE
         )
```

### {-}

We can see that income generated by region does not fluctuate from one year to the next, the proportions remain the same. However, we can notice that the average income does not differ much among regions, the gap is mainly created by the difference in the number of companies present in each region.

# Companies investments 

We will now have a look on investment made by company. 

## Data sources and description {.tabset .tabset-fade}

These data also comes from the website : [Newzoo.com](https://platform.newzoo.com/explorer).
We will use them to see if the amount of the investment is growing over the years and if certain factors can influence it. 

### Data overview

```{r}
# Load the data

data3 <- read_delim(file = here::here("data/NZ_CompaniesInvestmentscsv1.csv"), 
                    ";", escape_double = FALSE, col_names = FALSE, trim_ws = TRUE)

data4 <- read_delim(file = here::here("data/NZ_CompaniesInvestmentscsv2.csv"), 
                    ";", escape_double = FALSE, col_names = FALSE, trim_ws = TRUE)

# Data cleaning

# Data-set for visualization

CompaniesInvestments <- data3 %>%
  # combine the 2 data-sets
  full_join(data4) %>%
  # set a name for each variable
  rename(Date = X1, "Investment type" = X2, Sectors = X3, Emptycolumn = X4, Investee = X5, Amount = X6) %>%
  # modify the format of certain variable
  mutate(Date = dmy(Date), Emptycolumn = NULL, Sectors = str_replace_all(Sectors, ",.", ", "))

# Data-set for computation

numeric_amount <- c()
for(i in seq_along(CompaniesInvestments$Amount)){
  x <- parse_number(CompaniesInvestments$Amount[i])*(10 ** (3*as.integer(regexpr(str_sub(CompaniesInvestments$Amount[i], -1 , -1), 'KMB'))))
  numeric_amount <- c(numeric_amount, x)
}


numeric_CompInvest <- CompaniesInvestments %>% 
  mutate(Amount = numeric_amount, Date = floor_date(Date, "month"))

# Data overview

CompaniesInvestments %>% 
  kbl(caption = "Ammount of different investment") %>%
  kable_paper(full_width = F) %>% 
  scroll_box(width = "100%", height = "300px")
```

<p>&nbsp;</p>

We can see that these data consist of 653 observations of 5 attributes. 

Here is a description of each attribute :
   
- `Date` : date on which the investment was made
- `Investment type` : the type of the investment
- `Secors` : the sectors that received the investment
- `Investee` : the company that received the investment
- `Amount` : The amount of the investment

### Summary

```{r}
summary(numeric_CompInvest[, -c(1:4)])
```

<p>&nbsp;</p>

We can see here the basic statistics for the amount invested. They show a big gap between the min and the max, as well as between the mean and the median. We will try to determine the factors that influence these gaps.

## Exploratory Data Analysis

The table does not allow us to find any pattern in the investments amounts. To do so, we will look at `sectors` and the `investment type` separately and try see if can find any correlation between these variables and money invested. We also have to keep in mind that we don't have enough data to be really representative of reality, we will just try to define some trends.The following plots display the total amount of investments per month.

### Monthly investment {.tabset .tabset-fade}

#### Total

```{r}
Monthly_investment <- numeric_CompInvest %>% 
  mutate(Amount = numeric_amount, Date = floor_date(Date, "month")) %>% 
  group_by(Date) %>% 
  summarize(total = sum(Amount), 
            number = sum(Amount > 0), 
            mean = mean(Amount),
            median = median(Amount))

plot_ly(data = Monthly_investment,
        x = Monthly_investment$Date,
        y = ~Monthly_investment$total,
        type = "bar",
        height = 400) %>% 
  layout(title = "Monthly investment",
         xaxis = list(title = "Date"),
         yaxis = list(title = "Amount"),
         showlegend = FALSE)
```

#### Number

```{r}
plot_ly(data = Monthly_investment,
        x = Monthly_investment$Date,
        y = ~Monthly_investment$number,
        type = "bar",
        height = 400) %>% 
  layout(title = "Number of investment",
         xaxis = list(title = "Date"),
         yaxis = list(title = "Number"),
         showlegend = FALSE)
```

#### Mean

```{r}
plot_ly(data = Monthly_investment,
        x = Monthly_investment$Date,
        y = ~Monthly_investment$mean,
        type = "bar",
        height = 400) %>% 
  layout(title = "Monthly average investment",
         xaxis = list(title = "Date"),
         yaxis = list(title = "Amount"),
         showlegend = FALSE)
```

#### Median

```{r}
plot_ly(data = Monthly_investment,
        x = Monthly_investment$Date,
        y = ~Monthly_investment$median,
        type = "bar",
        height = 400) %>% 
  layout(title = "Monthly average investment",
         xaxis = list(title = "Date"),
         yaxis = list(title = "Amount"),
         showlegend = FALSE)
```

### {-}

With the exception of the number of investments made, time does not influence its amount, we can only say that there are more and more of them. Again, this is probably due to the lack of data contained in this data-set.

### The influence from the investment type {.tabset .tabset-fade}

#### Total

```{r}
investment_type <- CompaniesInvestments %>%
  rename(type = "Investment type") %>%
  mutate(Amount = numeric_amount) %>%
  group_by(type) %>%
  summarize(total = sum(Amount), 
            number = sum(Amount > 0), 
            mean = mean(Amount),
            median = median(Amount)) %>%
  arrange(desc(number))

plot_invest_type <- investment_type %>%
  mutate(type = factor(investment_type$type, 
                               levels = unique(investment_type$type)[order(investment_type$total, decreasing = FALSE)]))

plot_ly(data = plot_invest_type,
        x = plot_invest_type$total,
        y = ~plot_invest_type$type,
        color = ~plot_invest_type$type,
        colors = "Dark2",
        type = "bar",
        height = 400) %>% 
  layout(title = "Total investment in each type of investment",
         xaxis = list(title = "Amount"),
         yaxis = list(title = "Type of investment"),
         showlegend = FALSE)
```

#### Number

```{r}
plot_ly(data = plot_invest_type,
        x = plot_invest_type$number,
        y = ~plot_invest_type$type,
        color = ~plot_invest_type$type,
        colors = "Dark2",
        type = "bar",
        height = 400) %>% 
  layout(title = "Number of investment for each type",
         xaxis = list(title = "Number"),
         yaxis = list(title = "Type of investment"),
         showlegend = FALSE)
```

#### Mean

```{r}
plot_ly(data = plot_invest_type,
        x = plot_invest_type$mean,
        y = ~plot_invest_type$type,
        color = ~plot_invest_type$type,
        colors = "Dark2",
        type = "bar",
        height = 400) %>% 
  layout(title = "Average investment by type",
         xaxis = list(title = "Amount"),
         yaxis = list(title = "Type of investment"),
         showlegend = FALSE)
```

#### Median

```{r}
plot_ly(data = plot_invest_type,
        x = plot_invest_type$median,
        y = ~plot_invest_type$type,
        color = ~plot_invest_type$type,
        colors = "Dark2",
        type = "bar",
        height = 400) %>% 
  layout(title = "Median investment by type",
         xaxis = list(title = "Amount"),
         yaxis = list(title = "Type of investment"),
         showlegend = FALSE)
```

### {-}

Regarding the total amount invested, `Acquisition`, `Corporate`, `IPO` and `Venture` are largely those that generate the most money (about 82% of the total). However, we can observe that is not correlated with the mean amount invested, which can differ a lot among the type, independently of the ranking. The difference is mainly due to the number of investments made per type, not from the amount.


### The influence from the sector {.tabset .tabset-fade}

#### Number

```{r}
sector_influence <- CompaniesInvestments %>%
  mutate(Amount = numeric_amount) %>%
  separate(Sectors, into = c("s1", "s2", "s3", "s4", "s5"), sep = ",") %>%
  mutate(s2 = str_replace(s2, " ", ""),
         s3 = str_replace(s3, " ", ""),
         s4 = str_replace(s4, " ", ""),
         s5 = str_replace(s5, " ", "")) %>%
  pivot_longer(c(s1, s2, s3, s4, s5), names_to = "var", values_to = "Sectors") %>%
  drop_na(Sectors) %>%
  group_by(Sectors) %>%
  summarize(number = sum(Amount > 0),
            total = sum(Amount), 
            mean = mean(Amount),
            median = median(Amount)) %>%
  arrange(desc(total))

plot_sector_influence <- sector_influence %>%
  mutate(Sectors = factor(sector_influence$Sectors, 
                               levels = unique(sector_influence$Sectors)[order(sector_influence$number, decreasing = FALSE)]))

plot_ly(data = plot_sector_influence,
        x = plot_sector_influence$number,
        y = ~plot_sector_influence$Sectors,
        type = "bar",
        color = ~plot_sector_influence$Sectors,
        colors = "Dark2",
        height = 400) %>% 
  layout(title = "Number of investment for each sectors",
         xaxis = list(title = "Number"),
         yaxis = list(title = ""),
         showlegend = FALSE)
```

#### Mean

```{r}
plot_ly(data = plot_sector_influence,
        x = plot_sector_influence$mean,
        y = ~plot_sector_influence$Sectors,
        type = "bar",
        color = ~plot_sector_influence$Sectors,
        colors = "Dark2",
        height = 400) %>% 
  layout(title = "Average investment per sector",
         xaxis = list(title = "Amount"),
         yaxis = list(title = ""),
         showlegend = FALSE)
```

#### Median

```{r}
plot_ly(data = plot_sector_influence,
        x = plot_sector_influence$median,
        y = ~plot_sector_influence$Sectors,
        type = "bar",
        color = ~plot_sector_influence$Sectors,
        colors = "Dark2",
        height = 400) %>% 
  layout(title = "Median investment per sector",
         xaxis = list(title = "Amount"),
         yaxis = list(title = ""),
         showlegend = FALSE)
```

## Prediction

From these observations we can see that ...