---
title: "An overview of the NewZoo statistics"
author: "Mivelaz Allan"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: readable
    toc: true
    toc_float: true
    number_sections: true
    runtime: shiny
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
source(here::here("scripts/setup.R"))
```

# EDA for Company public revenue

Created in 2011, Twitch has become the number 1 platform for live-streaming. It is a social network that allows people to stream almost whatever they want. The main use on the platform is for gaming, it will therefore give us a strong indicator about the popularity of video games and the e-sport engagement.

## Data sources and description {.tabset .tabset-fade}

These data comes from the website : [Newzoo.com](https://platform.newzoo.com/explorer)
This website provides some general statistics about the use of Twitch, such as the time spend on watching/streaming videos for example. We will use this data to see the trends over time, and try to correlate them with the e-sport industry.

### Data overview

```{r}
# Load the data

data1 <- read_delim(file = here::here("data/NZ_CompaniesPublicRevenues2.csv"), ";", escape_double = FALSE, col_names = FALSE, trim_ws = TRUE)

numeric_Q1 <- c()
for(i in seq_along(data1$X3)){
  x <- parse_number(data1$X3[i])*(10 ** (3*as.integer(regexpr(str_sub(data1$X3[i], -1 , -1), 'KMB'))))
  numeric_Q1 <- c(numeric_Q1, x)
}

numeric_Q2 <- c()
for(i in seq_along(data1$X4)){
  x <- parse_number(data1$X4[i])*(10 ** (3*as.integer(regexpr(str_sub(data1$X4[i], -1 , -1), 'KMB'))))
  numeric_Q2 <- c(numeric_Q2, x)
}

numeric_Q3 <- c()
for(i in seq_along(data1$X5)){
  x <- parse_number(data1$X5[i])*(10 ** (3*as.integer(regexpr(str_sub(data1$X5[i], -1 , -1), 'KMB'))))
  numeric_Q3 <- c(numeric_Q3, x)
}

numeric_Q4 <- c()
for(i in seq_along(data1$X6)){
  x <- parse_number(data1$X6[i])*(10 ** (3*as.integer(regexpr(str_sub(data1$X6[i], -1 , -1), 'KMB'))))
  numeric_Q4 <- c(numeric_Q4, x)
}

numeric_Q1_2020 <- c()
for(i in seq_along(data1$X7)){
  x <- parse_number(data1$X7[i])*(10 ** (3*as.integer(regexpr(str_sub(data1$X7[i], -1 , -1), 'KMB'))))
  numeric_Q1_2020 <- c(numeric_Q1_2020, x)
}

numeric_Q2_2020 <- c()
for(i in seq_along(data1$X8)){
  x <- parse_number(data1$X8[i])*(10 ** (3*as.integer(regexpr(str_sub(data1$X8[i], -1 , -1), 'KMB'))))
  numeric_Q2_2020 <- c(numeric_Q2_2020, x)
}

CompRev <- data1 %>%
  # set a name for each variable
  rename(Company_name = X1, Region_of_HQ = X2, Q1 = X3, 
         Q2 = X4, Q3 = X5, Q4 = X6, 
         Q1_2020 = X7, Q2_2020 = X8) %>%
  # modify the format of certain variable   
  mutate(Q1 = numeric_Q1, Q2 = numeric_Q2,
         Q3 = numeric_Q3, Q4 = numeric_Q4,
         Q1_2020 = numeric_Q1_2020, Q2_2020 = numeric_Q2_2020) %>%
  # compute total and growth
  mutate(Total_2019 = Q1 + Q2 + Q3 + Q4, .after = Q4) %>%
  mutate(Half_2020 = Q1_2020 + Q2_2020, .after = Q2_2020) %>%
  mutate(Q1_grate = 100*(Q1_2020 - Q1)/Q1, .after = Q1_2020) %>% 
  mutate(Q2_grate = 100*(Q2_2020 - Q2)/Q2, .after = Q2_2020)

CompRev2 <- CompRev %>%
  mutate(Q1 = data1$X3, Q2 = data1$X4, Q3 = data1$X5,
         Q4 = data1$X6, Q1_2020 = data1$X5, Q2_2020 = data1$X6,
         Total_2019 = ifelse(Total_2019 >= 1000000000, 
                             f_bills(Total_2019, prefix = "$", digits = 12), 
                             f_mills(Total_2019, prefix = "$", digits = 9)),
         Half_2020 = ifelse(Half_2020 >= 1000000000, 
                            f_bills(Half_2020, prefix = "$", digits = 12), 
                            f_mills(Half_2020, prefix = "$", digits = 9)),
         Q1_grate = paste0(round(Q1_grate, digits = 2), "%"), 
         Q2_grate = paste0(round(Q2_grate, digits = 2), "%"))

# ------------------------------------------------------------------------------

# Data overview 

CompRev2 %>%
  rename("Company name" = Company_name, "Region of HQ" = Region_of_HQ,
         "Q1 " = Q1_2020, "Q2 " = Q2_2020, "Full year" = Total_2019, 
         "YoY growth" = Q1_grate,"Half year " = Half_2020, 
         "YoY growth " = Q2_grate) %>%
  kbl(caption = "Game revenu per company") %>%
  kable_paper(full_width = F) %>% 
  add_header_above(c(" " = 2, "2019" = 5, "2020" = 5)) %>%
  scroll_box(width = "100%", height = "300px")
```

<p>&nbsp;</p>
`CompaniesPublicRevenues.csv` contains the revenue of the top 25 game companies for several period, where `Q1`, `Q2`, `Q3` and `Q4` correspond to every quarter of the year. For example, we can see which company generated most income in 2019.

### Summary

```{r}
# General statistics for the numeric variable

summary(CompRev[, -c(1,2)] %>% rename("Income in 2019 (Q1)" = Q1,
         "Income in 2019 (Q2)" = Q2,
         "Income in 2019 (Q3)" = Q3,
         "Income in 2019 (Q4)" = Q4,
         "Total income in 2019" = Total_2019,
         "Income in 2020 (Q1)" = Q1_2020,
         "YoY growth rate in Q1" = Q1_grate,
         "Income in 2020 (Q2)" = Q2_2020,
         "YoY growth rate in Q2" = Q2_grate,
         "Income for the first half of 2020" = Half_2020
         ))
```

<p>&nbsp;</p>

We can see here the basic statistics for every variable. They show a big gap between the min and the max, as well as between the mean and the median. We will try to determine the factors that influence these gaps. Finally, with the exception of `Active_streamers`, we have no issue with NA. (see 1.1.3 Missing value for more information)

<p>&nbsp;</p>

## Exploratory Data Analysis

We can see from the table that our data are growing over time. To have a better view on the evolution, let's have a look at each variable separately. The following plots display the statistics for every variable per month.

### Income per company {.tabset .tabset-fade}

#### Total income in 2019

```{r}
plot_CompRev <- CompRev %>%
  mutate(Company_name = factor(CompRev$Company_name, 
                               levels = unique(CompRev$Company_name)[order(CompRev$Total_2019, decreasing = FALSE)]))

plot_ly(data = plot_CompRev,
        x = plot_CompRev$Total_2019,
        y = ~plot_CompRev$Company_name,
        color = ~plot_CompRev$Company_name,
        colors = "Dark2",
        type = "bar",
        height = 600) %>% 
  layout(title = "Income per company",
         xaxis = list(title = "Revenue"),
         yaxis = list(title = ""),
         showlegend = FALSE)
```

#### Total income in 2020

```{r}
plot_CompRev_2020 <- CompRev %>%
  mutate(Company_name = factor(CompRev$Company_name, 
                               levels = unique(CompRev$Company_name)[order(CompRev$Total_2019, decreasing = FALSE)]))

plot_ly(data = plot_CompRev_2020,
        x = plot_CompRev_2020$Half_2020,
        y = ~plot_CompRev_2020$Company_name,
        color = ~plot_CompRev_2020$Company_name,
        colors = "Dark2",
        type = "bar",
        height = 600) %>% 
  layout(title = "Income per company",
         xaxis = list(title = "Revenue"),
         yaxis = list(title = ""),
         showlegend = FALSE)
```

#### YoY growth rate

```{r}
YoY <- CompRev %>%
  mutate(Q1_grate = (round(Q1_grate, digits = 2)),
         Company_name = factor(CompRev$Company_name, 
                               levels = unique(CompRev$Company_name)[order(CompRev$Q1_grate, decreasing = FALSE)]))

# Q1 growth rate
plot1 <- plot_ly(YoY, x = ~Q1_grate, y = ~Company_name, type = "bar", name = 'YoY growth for Q1 (%)', height = 500, width = 800) %>% 
  layout(title = "",
         xaxis = list(title = "Growth rate (%)"),
         yaxis = list(title = ""),
         showlegend = FALSE)

# Q1 growth rate
plot2 <- plot_ly(YoY, x = ~Q2_grate, y = ~Company_name, type = "bar", name = 'Yoy growth for Q2 (%)', height = 500, width = 800) %>% 
  layout(title = "",
         xaxis = list(title = "Growth rate (%)"),
         yaxis = list(title = ""),
         showlegend = FALSE)

plot <- subplot(plot1, plot2, margin = 0, shareY = TRUE, titleX = T)

plot
```

### Mean and total income per region {.tabset .tabset-fade}

#### 2019 full year

```{r}
CompRev_HQ2019 <- CompRev %>% 
  mutate(Region_of_HQ = factor(CompRev$Region_of_HQ, 
                               levels = unique(CompRev$Region_of_HQ)[order(CompRev$Total_2019, decreasing = FALSE)])) 

plot_CompRev_HQ2019 <- CompRev_HQ2019 %>%
  group_by(Region_of_HQ) %>% 
  summarize(total = sum(Total_2019), 
            number = sum(Total_2019 > 0), 
            mean = mean(Total_2019),
            median = median(Total_2019))

plot_ly(data = plot_CompRev_HQ2019,
        x = plot_CompRev_HQ2019$Region_of_HQ,
        y = ~plot_CompRev_HQ2019$mean,
        color = ~plot_CompRev_HQ2019$Region_of_HQ,
        colors = "Dark2",
        type = "bar",
        name = "Total income",
        height = 400) %>% 
  add_trace(y = ~plot_CompRev_HQ2019$total, name = 'Mean') %>%
  layout(title = "Income per Region",
         xaxis = list(title = "Revenue"),
         yaxis = list(title = ""),
         margin = list(b = 0),
         barmode = "group",
         showlegend = FALSE)
```

#### 2020 half year

```{r}
CompRev_HQ2020 <- CompRev %>% 
  mutate(Region_of_HQ = factor(CompRev$Region_of_HQ, 
                               levels = unique(CompRev$Region_of_HQ)[order(CompRev$Total_2019, decreasing = FALSE)])) 

plot_CompRev_HQ2020 <- CompRev_HQ2020 %>%
  group_by(Region_of_HQ) %>% 
  summarize(total = sum(Half_2020),
            number = sum(Half_2020 > 0), 
            mean = mean(Half_2020),
            median = median(Half_2020))

plot_ly(data = plot_CompRev_HQ2020,
        x = plot_CompRev_HQ2020$Region_of_HQ,
        y = ~plot_CompRev_HQ2020$mean,
        color = ~plot_CompRev_HQ2020$Region_of_HQ,
        colors = "Dark2",
        type = "bar",
        name = "Total income",
        height = 400) %>% 
  add_trace(y = ~plot_CompRev_HQ2020$total, name = 'Mean') %>%
  layout(title = "Income per Region",
         xaxis = list(title = "Revenue"),
         yaxis = list(title = ""),
         margin = list(b = 0),
         barmode = "group",
         showlegend = FALSE)
```


# NewZoo Campanies Investments 

dasnfjknsdkjfndsfasf

## Data sources and description {.tabset .tabset-fade}

These data comes from the website : Newzoo.com This website provides some general statistics about the use of Twitch, such as the time spend on watching/streaming videos for example. We will use this data to see the trends over time, and try to correlate them with the e-sport industry.

### Data overview

```{r}
# Load the data

data3 <- read_delim(file = here::here("data/NZ_CompaniesInvestmentscsv1.csv"), 
                    ";", escape_double = FALSE, col_names = FALSE, trim_ws = TRUE)

data4 <- read_delim(file = here::here("data/NZ_CompaniesInvestmentscsv2.csv"), 
                    ";", escape_double = FALSE, col_names = FALSE, trim_ws = TRUE)

# Data cleaning

# Data-set for visualization

CompaniesInvestments <- data3 %>%
  # combine the 2 data-sets
  full_join(data4) %>%
  # set a name for each variable
  rename(Date = X1, "Investment type" = X2, Sectors = X3, Emptycolumn = X4, Investee = X5, Amount = X6) %>%
  # modify the format of certain variable
  mutate(Date = dmy(Date), Emptycolumn = NULL, Sectors = str_replace_all(Sectors, ",.", ", "))

# Data-set for computation

numeric_amount <- c()
for(i in seq_along(CompaniesInvestments$Amount)){
  x <- parse_number(CompaniesInvestments$Amount[i])*(10 ** (3*as.integer(regexpr(str_sub(CompaniesInvestments$Amount[i], -1 , -1), 'KMB'))))
  numeric_amount <- c(numeric_amount, x)
}


numeric_CompInvest <- CompaniesInvestments %>% 
  mutate(Amount = numeric_amount, Date = floor_date(Date, "month"))

# Data overview

CompaniesInvestments %>% 
  kbl(caption = "Ammount of different investment") %>%
  kable_paper(full_width = F) %>% 
  scroll_box(width = "100%", height = "300px")
```

<p>&nbsp;</p>
`CompaniesInvestment.csv` contains the amount of several investment. It will be usefull to see if the amount is growing over the years and if depends on several factor such as the `Sectors` or the `Investment type`.

### Summary

```{r}
summary(numeric_CompInvest[, -c(1:4)])
```

No pattern, let's try ot find one !

<p>&nbsp;</p>

## Exploratory Data Analysis

We can see from the table that our data are growing over time. To have a better view on the evolution, let's have a look at each variable separately. The following plots display the statistics for every variable per month.

### Monthly investment {.tabset .tabset-fade}

#### Total

```{r}
Monthly_investment <- numeric_CompInvest %>% 
  mutate(Amount = numeric_amount, Date = floor_date(Date, "month")) %>% 
  group_by(Date) %>% 
  summarize(total = sum(Amount), 
            number = sum(Amount > 0), 
            mean = mean(Amount))

plot_ly(data = Monthly_investment,
        x = Monthly_investment$Date,
        y = ~Monthly_investment$total,
        type = "bar",
        height = 400) %>% 
  layout(title = "Monthly investment",
         xaxis = list(title = "Date"),
         yaxis = list(title = "Amount"),
         showlegend = FALSE)
```

#### Number

```{r}
plot_ly(data = Monthly_investment,
        x = Monthly_investment$Date,
        y = ~Monthly_investment$number,
        type = "bar",
        height = 400) %>% 
  layout(title = "Number of investment",
         xaxis = list(title = "Date"),
         yaxis = list(title = "Number"),
         showlegend = FALSE)
```

#### Mean

```{r}
plot_ly(data = Monthly_investment,
        x = Monthly_investment$Date,
        y = ~Monthly_investment$mean,
        type = "bar",
        height = 400) %>% 
  layout(title = "Monthly average investment",
         xaxis = list(title = "Date"),
         yaxis = list(title = "Amount"),
         showlegend = FALSE)
```

### The influence from the sector {.tabset .tabset-fade}

#### Total

```{r}
investment_type <- CompaniesInvestments %>%
  rename(type = "Investment type") %>%
  mutate(Amount = numeric_amount) %>%
  group_by(type) %>%
  summarize(total = sum(Amount), 
            number = sum(Amount > 0), 
            mean = mean(Amount)) %>%
  arrange(desc(number))

plot_invest_type <- investment_type %>%
  mutate(type = factor(investment_type$type, 
                               levels = unique(investment_type$type)[order(investment_type$total, decreasing = FALSE)]))

plot_ly(data = plot_invest_type,
        x = plot_invest_type$total,
        y = ~plot_invest_type$type,
        type = "bar",
        height = 400) %>% 
  layout(title = "Monthly average investment",
         xaxis = list(title = "Amount"),
         yaxis = list(title = "Type of investment"),
         showlegend = FALSE)
```

#### Number

```{r}
plot_ly(data = plot_invest_type,
        x = plot_invest_type$number,
        y = ~plot_invest_type$type,
        type = "bar",
        height = 400) %>% 
  layout(title = "Monthly average investment",
         xaxis = list(title = "Amount"),
         yaxis = list(title = "Type of investment"),
         showlegend = FALSE)
```

#### Mean

```{r}
plot_ly(data = plot_invest_type,
        x = plot_invest_type$mean,
        y = ~plot_invest_type$type,
        type = "bar",
        height = 400) %>% 
  layout(title = "Monthly average investment",
         xaxis = list(title = "Amount"),
         yaxis = list(title = "Type of investment"),
         showlegend = FALSE)
```

### The influence from the investment type {.tabset .tabset-fade}

#### Investment type

```{r}
sector_influence <- CompaniesInvestments %>%
  mutate(Amount = numeric_amount) %>%
  separate(Sectors, into = c("s1", "s2", "s3", "s4", "s5"), sep = ",") %>%
  mutate(s2 = str_replace(s2, " ", ""),
         s3 = str_replace(s3, " ", ""),
         s4 = str_replace(s4, " ", ""),
         s5 = str_replace(s5, " ", "")) %>%
  pivot_longer(c(s1, s2, s3, s4, s5), names_to = "var", values_to = "Sectors") %>%
  drop_na(Sectors) %>%
  group_by(Sectors) %>%
  summarize(number = sum(Amount > 0),
            total = sum(Amount), 
            mean = mean(Amount),
            median = median(Amount)) %>%
  arrange(desc(total))

plot_sector_influence <- sector_influence %>%
  mutate(Sectors = factor(sector_influence$Sectors, 
                               levels = unique(sector_influence$Sectors)[order(sector_influence$number, decreasing = FALSE)]))

plot_ly(data = plot_sector_influence,
        x = plot_sector_influence$number,
        y = ~plot_sector_influence$Sectors,
        type = "bar",
        height = 400) %>% 
  layout(title = "Monthly average investment",
         xaxis = list(title = "Amount"),
         yaxis = list(title = "Type of investment"),
         showlegend = FALSE)
```

#### Mean

```{r}
plot_ly(data = plot_sector_influence,
        x = plot_sector_influence$mean,
        y = ~plot_sector_influence$Sectors,
        type = "bar",
        height = 400) %>% 
  layout(title = "Monthly average investment",
         xaxis = list(title = "Amount"),
         yaxis = list(title = "Type of investment"),
         showlegend = FALSE)
```

#### Median

```{r}
plot_ly(data = plot_sector_influence,
        x = plot_sector_influence$median,
        y = ~plot_sector_influence$Sectors,
        type = "bar",
        height = 400) %>% 
  layout(title = "Monthly average investment",
         xaxis = list(title = "Amount"),
         yaxis = list(title = "Type of investment"),
         showlegend = FALSE)
```