---
title: "An overview of the twitch platform"
author: "Mivelaz Allan"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: readable
    toc: true
    toc_float: true
    number_sections: true
    runtime: shiny
---

```{r, echo = FALSE, message = FALSE, include=FALSE}
source(here::here("scripts/setup.R"))
```

# Twitch Statistic 

Created in 2011, Twitch has become the number 1 platform for live-streaming. It is a social network that allows people to stream almost whatever they want. The main use on the platform is for gaming, it will therefore give us a strong indicator about the popularity of video games and the e-sport engagement.

## Data sources and description {.tabset .tabset-fade}

We accessed data about Twitch statistics on the website [twitchtracker.com](https://twitchtracker.com/statistics).

This website provides some general statistics about the use of Twitch, such as the time spend on watching/streaming videos for example. We will use this data to see the trends over time, and try to correlate them with the e-sport industry.

### Data overview

```{r}
data1 <- read_delim(file = here::here("data/Twitch.csv"), ";", 
                    escape_double = FALSE, col_names = FALSE, trim_ws = TRUE)

# Data cleaning

TwitchData <- data1 %>%
  # set a name for each variable
  rename(Date = X1, Avg_concur_viewers = X2, 
         Avg_concur_channels = X3, Hours_watched = X4, 
         Active_streamers = X5, Hours_streamed = X6) %>%
  # modify the format of certain variable
  mutate(Date = mdy(Date), 
         Hours_watched = parse_number(Hours_watched)*1000000) %>%
  # Replace value with NA (in our dataframe, n/a are considered as character)
  replace_with_na(replace = list(Active_streamers = "n/a")) %>%
  mutate(Viewers_per_streamer = Hours_watched/Hours_streamed) %>%
  # Convert the column from character to double
  mutate(Active_streamers = parse_number(Active_streamers))

# Data overview

TwitchData %>%
  # shows values in a more aesthetic way
  mutate(Date = data1$X1,
         Avg_concur_viewers = case_when(Avg_concur_viewers >= 1000000000 ~ f_bills(Avg_concur_viewers, digits = 12),
                                                     Avg_concur_viewers >= 1000000 & Avg_concur_viewers < 1000000000 ~ f_mills(Avg_concur_viewers, digits = -4),
                                                     Avg_concur_viewers < 1000000 & Avg_concur_viewers >= 1000 ~ f_thous(Avg_concur_viewers, digits = 6)),
         Avg_concur_channels = case_when(Avg_concur_channels >= 1000000000 ~ f_bills(Avg_concur_channels, digits = 12),
                                         Avg_concur_channels >= 1000000 & Avg_concur_channels < 1000000000 ~ f_mills(Avg_concur_channels, digits = 9),
                                         Avg_concur_channels < 1000000 & Avg_concur_channels >= 1000 ~ f_thous(Avg_concur_channels, digits = -2)),
         Hours_watched = case_when(Hours_watched >= 1000000000 ~ f_bills(Hours_watched, digits = -7),
                                   Hours_watched >= 1000000 & Hours_watched < 1000000000 ~ f_mills(Hours_watched, digits = -3),
                                   Hours_watched < 1000000 & Hours_watched >= 1000 ~ f_thous(Hours_watched, digits = 6)),
         Active_streamers = case_when(Active_streamers >= 1000000000 ~ f_bills(Active_streamers, digits = 12),
                                      Active_streamers >= 1000000 & Active_streamers < 1000000000 ~ f_mills(Active_streamers, digits = -4),
                                      Active_streamers < 1000000 & Active_streamers >= 1000 ~ f_thous(Active_streamers, digits = 6)),
         Hours_streamed = case_when(Hours_streamed >= 1000000000 ~ f_bills(Hours_streamed, digits = 12),
                                    Hours_streamed >= 1000000 & Hours_streamed < 1000000000 ~ f_mills(Hours_streamed, digits = -4),
                                    Hours_streamed < 1000000 & Hours_streamed >= 1000 ~ f_thous(Hours_streamed, digits = 6)),
         Viewers_per_streamer = round(Viewers_per_streamer, digits = 1)) %>%
  rename("Concurrent viewers" = Avg_concur_viewers,
         "Concurrent channels" = Avg_concur_channels,
         "Active channels" = Active_streamers,
         "Hours watched" = Hours_watched,
         "Hours streamed" = Hours_streamed,
         "Viewers per streamer" = Viewers_per_streamer) %>%
  kbl(caption = "Twitch statistics") %>%  
  kable_paper(full_width = F) %>%
  kable_styling(bootstrap_options  = c("striped", "hover")) %>%
  scroll_box(width = "100%", height = "300px")
```

<p>&nbsp;</p>

We can see that these data consist of 99 observations of 7 attributes. 

Here is a description of each attribute :
   
- `Date` : month in which the data apply
- `Concurrent viewers` : Number of viewers connected at the same time on average 
- `Concurrent channels` : Number of channels connected at the same time on average 
- `Hours watched` : Total number of hours watched
- `Active channels` : Total number of active channels
- `Hours streamed` : Total number of hours streamed
- `Viewers per streamer` : Average number of viewers per streamer

### Summary 

```{r}
# Summary

summary(TwitchData[, -1] %>% rename("Concurrent viewers" = Avg_concur_viewers,
         "Concurrent channels" = Avg_concur_channels,
         "Active channels" = Active_streamers,
         "Hours watched" = Hours_watched,
         "Hours streamed" = Hours_streamed,
         "Viewers per streamer" = Viewers_per_streamer))
```

<p>&nbsp;</p>

We can see here the basic statistics for every variable. They show a big gap between the min and the max, as well as between the mean and the median. We will try to determine the factors that influence these gaps. Finally, with the exception of `Active_streamers`, we have no issue with NA. (see 1.1.3 Missing value for more information)

### Missing value

```{r}
freq.na(TwitchData)
```

<p>&nbsp;</p>

This table gives the number of NA for each variable with its proportion. The amount of NA for the `Active_streamers` mostly come from missing value before 2015. Thus, we are still able to use this variable, we will just reduce the time period to analyze.  

<p>&nbsp;</p>

## Exploratory Data Analysis

We can see from the table that our data are growing over time. To have a better view on the evolution, let's have a look at each variable separately. The following plots display the statistics for every variable per month.

### Variable over time {.tabset .tabset-fade}

#### Average concurent viewers

```{r}

library(shiny)

shiny_twitch <- TwitchData %>%
  pivot_longer(c(Avg_concur_viewers, Avg_concur_channels, Hours_watched, Active_streamers, Hours_streamed, Viewers_per_streamer),
               names_to = "Variable",
               values_to = "Value")

ui<- fluidPage(
  titlePanel("Interactive plot for the Twitch statistics"),
  selectInput(inputId = "Variable",
              label="Choose a Variable",
             choices = c("Avg_concur_viewers", "Avg_concur_viewers","Hours_watched", "Active_streamers", "Hours_streamed", "Viewers_per_streamer")),
  mainPanel(
    h1("Statistics over time"),
    textOutput("Selected_variable"),
    plotlyOutput(outputId ="PlotlyVariable")
))



server <- function(input,output)
  {
  data <- reactive({
    shiny_twitch %>% filter(Variable == input$Variable)})

   output$Selected_variable <- renderUI({
    paste("You have selected", input$Variable)
  })
   output$PlotlyVariable <- renderPlotly({
       plot_ly(data(), x = ~Date, y = ~Value ,type = "bar", width = 600
               ,name = "Number", height = 400) %>% 
      layout(
         yaxis = list(showline = FALSE, side = "right" ,title = "", color = "blue")
         ,xaxis = list( showline = FALSE, zeroline = FALSE, dtick = 0, title = "Date")
         ,showlegend = TRUE ,margin = list(pad = 30, b = 30, l = 150, r = 30)
         ,legend = list(orientation = "bottomright"))
     
})
}

shinyApp(ui, server)
```

```{r}
plot_ly(type = "bar",
        x = TwitchData$Date, 
        y = TwitchData$Avg_concur_viewers,
        height = 400) %>%
  layout(xaxis = list(title="Date"),
         title = "Average concurent viewers increasing over time")
```

#### Average concurent channels

```{r}
plot_ly(type = "bar",
        x = TwitchData$Date, 
        y = TwitchData$Avg_concur_channels,
        height = 400) %>%
  layout(xaxis = list(title="Date"),
         title = "Average concurent channels increasing over time")
```

#### Total number of hours watched per month

```{r}
plot_ly(type = "bar",
        x = TwitchData$Date, 
        y = TwitchData$Hours_watched,
        height = 400) %>%
  layout(xaxis = list(title="Date"),
         title = "Total Hours watched increasing over time")
```

#### Total number of active channels

```{r}
plot_ly(type = "bar",
        x = TwitchData$Date, 
        y = TwitchData$Active_streamers,
        height = 400) %>%
  layout(xaxis = list(title="Date"),
         title = "Total number of active streamers increasing over time")
```

#### Total number of hours streamed per month

```{r}
plot_ly(type = "bar",
        x = TwitchData$Date, 
        y = TwitchData$Hours_streamed,
        height = 400) %>%
  layout(xaxis = list(title="Date"),
         title = "Total number of hours streamed increasing over time")
```

Total number of hours streamed over the time

#### Average number of viewers per streamer per month

```{r}
plot_ly(type = "bar",
        x = TwitchData$Date, 
        y = TwitchData$Viewers_per_streamer,
        height = 400) %>%
  layout(xaxis = list(title="Date"),
         title = "Viewers per streamer on average decreasing over time")
```

Viewers per streamer on average over the time 

<hr/>

### {-}

From these observations, we can identify several pattern :

- Every variable (we do not include `viewers per streamer` in it because it is a ratio) is increasing over time. It is increasing in a linear way between 2012 and February 2020, following by a jump in early 2020.
- This jump partly explains the gap between the mean and the median : the last few months are very high relative to the others, which increases the mean but leaves the median unchanged.
- The only plot that is decreasing over time is the one showing the ratio between `Hours watched` and `Hours streamed`. This means that even both are growing, they are not growing at the same rate : they are more new streamers than new watchers.

Now some dynamic plot to display our idea.

### Dynamic graph {.tabset .tabset-fade}

Here are some dynamic plots. Although they do not add any value, it is nice to look at them. 

#### Comparaison

```{r}
plot_ly(data = TwitchData, x = ~TwitchData$Date, y = ~TwitchData$Hours_watched
        ,type = "scatter", mode = "lines", width = 800
        ,name = "Hours watched", height = 400) %>%
  add_trace(x = ~TwitchData$Date, y = ~TwitchData$Hours_streamed, yaxis = "y2", name = "Hours streamed") %>%
  add_trace(x = ~TwitchData$Date, y = ~TwitchData$Viewers_per_streamer, yaxis = "y3", name = "Viewers per steamers")%>%
  layout(
    yaxis = list(
      showline = FALSE, side = "left"
      ,title = ""
      , color = "blue"
    )
    ,yaxis2 = list(
      showline = FALSE
      ,overlaying = "y"
      ,title = ""
      , anchor = "free"
      , color = "orange"
    )
    ,yaxis3 = list(
      showline = FALSE,
      side = "right",
      overlaying = "y"
      ,title = ""
      , color = "green"
    )
    ,xaxis = list(
      showline = FALSE, zeroline = FALSE, dtick = 0, title = "Date"
    )
    ,showlegend = TRUE
    ,margin = list(
      pad = 30, b = 90, l = 150, r = 90
    )
    ,legend = list(orientation = "v")
    , title = "Comparaison between watched and streamed"
  )
```
Here, we have gathered the statistics for `Hours watched`, `Hours streamed` and `Viewers per streamer`. It allows you to see  in a single graph the general trends between the people who create content and those who watch it.

#### Step by step

```{r}
# Create function to set the frame 

accumulate_by <- function(dat, var) {
  var <- lazyeval::f_eval(var, dat)
  lvls <- plotly:::getLevels(var)
  dats <- lapply(seq_along(lvls), function(x) {
    cbind(dat[var %in% lvls[seq(1, x)], ], frame = lvls[[x]])
  })
  dplyr::bind_rows(dats)
}


# Arrange the actual data-set

bf <- TwitchData %>% separate(Date, into = c("year", "month", "day")) %>%
  mutate(day = NULL) %>% 
  unite(Date, year, month, sep = "-") %>% 
  arrange(Date) %>% mutate(ID = 1:99) %>% 
  accumulate_by(~ID)

# Build the dynamic plot
ggplotly(ggplot(bf, aes(ID, Hours_streamed, frame = frame)) +
                  geom_line(), height = 400) %>%
  layout(
    title = "Hours watched",
    yaxis = list(
      title = "",
      zeroline = F,
      tickprefix = "$"
    ),
    xaxis = list(
      title = "Month",
      zeroline = F, 
      showgrid = F
    )
  ) %>% 
  animation_opts(
    frame = 30, 
    transition = 0, 
    redraw = FALSE
  ) %>%
  animation_slider(
    currentvalue = list(
      prefix = "Month "
  )
)


```

This interactive plot does not display all the value from the beginning. In this way, one can really feel the evolution over time, the effect is even more striking.

## Prediction

We can draw the following based on these observations :

- More and more people are attracted by video games, this industry is on a perpetual growth since the beginning of 2000 and it is not about to stop. Twitch certainly has a bright future.
- Beware, however, of the March 2020 jump : it mostly comes from the corona-virus and people stuck at home, we do not expect the audience to grow at a significant rate in the coming months, since a lot of people have already arrived at this time. Although we believe that the data will continue to increase in the long term, it is very likely that it will flatten for a period of time, or even decrease.
- As we have seen, the number of viewers per streamer is decreasing, indicating that for each new channel, there is not enough new viewers to keep the same ratio : it became harder to find new member, maybe the network is a bit saturated. 