## EDA for Twitch data-set

These data comes from the website : [Twitchtracker](https://twitchtracker.com/statistics)

```{r, echo=FALSE, warning=FALSE, message=FALSE}
source(here::here("scripts/setup.R"))
```

```{r}
data1 <- read_delim(file = here::here("data/Twitch.csv"), ";", 
                    escape_double = FALSE, col_names = FALSE, trim_ws = TRUE)
```

Let's first load the dataset :

```{r}
# Data cleaning

TwitchData <- data1 %>%
  # set a name for each variable
  rename(Date = X1, Avg_concur_viewers = X2, 
         Avg_concur_channels = X3, Hours_watched = X4, 
         Active_streamers = X5, Hours_streamed = X6) %>%
  # modify the format of certain variable
  mutate(Date = mdy(Date), 
         Hours_watched = parse_number(Hours_watched)*1000000,
         Hours_streamed = Hours_streamed) %>%
  # Replace value with NA (in our dataframe, n/a are considered as character)
  replace_with_na(replace = list(Active_streamers = "n/a")) %>%
  mutate(Viewers_per_streamer = Hours_watched*100000000/Hours_streamed) %>%
  # Convert the column from character to double
  mutate(Active_streamers = parse_number(Active_streamers))

# Data overview

TwitchData %>% 
   kbl(caption = "Twitch statistics") %>%  
   kable_paper(full_width = F) %>% 
   scroll_box(width = "100%", height = "300px")

# test 
freq.na(TwitchData)
```
<p>&nbsp;</p>
We can see that these data consist of 99 observations of 7 attributes. 

## Here is a description of each attribute :
   
- `Date` : month in which the data apply
- `Avg_concur_viewers` : Number of viewers connected in the same time in average 
- `Avg_concur_channels` : Number of channels connected in the same time in average 
- `Hours_watched` (in million) : Total number of hours watched per month
- `Active_streamers` : Total number of active channels
- `Hours_streamed` : Total number of hours streamed per month
- `Viewers_per_streamer` : Average number of viewers per streamer per month


## Here the graph for each variable :

##### Average concurent viewers for each month :

```{r}
plot_ly(type = "bar",
        x = TwitchData$Date, 
        y = TwitchData$Avg_concur_viewers,
        height = 400) %>%
  layout(xaxis = list(title="Date"),
         title = "Average concurent viewers")
```

##### Average concurent channels for each month:

```{r}
plot_ly(type = "bar",
        x = TwitchData$Date, 
        y = TwitchData$Avg_concur_channels,
        height = 400) %>%
  layout(xaxis = list(title="Date"),
         title = "Average concurent channels")
```

##### Total number of hours watched per month :

```{r}
plot_ly(type = "bar",
        x = TwitchData$Date, 
        y = TwitchData$Hours_watched,
        height = 400) %>%
  layout(xaxis = list(title="Date"),
         title = "Total Hours watched")
```

##### Total number of active channels

```{r}
plot_ly(type = "bar",
        x = TwitchData$Date, 
        y = TwitchData$Active_streamers,
        height = 400) %>%
  layout(xaxis = list(title="Date"),
         title = "Total number of active streamers")
```

##### Total number of hours streamed per month

```{r}
plot_ly(type = "bar",
        x = TwitchData$Date, 
        y = TwitchData$Hours_streamed,
        height = 400) %>%
  layout(xaxis = list(title="Date"),
         title = "Total number of hours streamed")
```

##### Average number of viewers per streamer per month

```{r}
plot_ly(type = "bar",
        x = TwitchData$Date, 
        y = TwitchData$Viewers_per_streamer,
        height = 400) %>%
  layout(xaxis = list(title="Date"),
         title = "Viewers per streamer on average")
```

```{r}
plot_ly(data = TwitchData, x = ~TwitchData$Date, y = ~TwitchData$Hours_watched
        ,type = "scatter", mode = "lines", width = 800
        ,name = "Hours watched", height = 400) %>%
  add_trace(x = ~TwitchData$Date, y = ~TwitchData$Hours_streamed, yaxis = "y2", name = "Hours streamed") %>%
  add_trace(x = ~TwitchData$Date, y = ~TwitchData$Viewers_per_streamer, yaxis = "y3", name = "Viewers per steamers")%>%
  layout(
    yaxis = list(
      showline = FALSE, side = "left"
      ,title = ""
      , color = "blue"
    )
    ,yaxis2 = list(
      showline = FALSE
      ,overlaying = "y"
      ,title = ""
      , anchor = "free"
      , color = "orange"
    )
    ,yaxis3 = list(
      showline = FALSE,
      side = "right",
      overlaying = "y"
      ,title = ""
      , color = "green"
    )
    ,xaxis = list(
      showline = FALSE, zeroline = FALSE, dtick = 0, title = "Date"
    )
    ,showlegend = TRUE
    ,margin = list(
      pad = 30, b = 90, l = 150, r = 90
    )
    ,legend = list(orientation = "v")
    , title = "Comparaison between watched and streamed"
  )
```


```{r}
bf <- TwitchData %>% separate(Date, into = c("year", "month", "day")) %>%
  filter(year >= 2017) %>% mutate(day = NULL) %>% 
  unite(Date, year, month, sep = "-") %>% 
  arrange(Date) %>% mutate(ID = 1:47)
bf$ID <- seq.int(nrow(bf))


accumulate_by <- function(dat, var) {
  var <- lazyeval::f_eval(var, dat)
  lvls <- plotly:::getLevels(var)
  dats <- lapply(seq_along(lvls), function(x) {
    cbind(dat[var %in% lvls[seq(1, x)], ], frame = lvls[[x]])
  })
  dplyr::bind_rows(dats)
}

bf <- bf %>%
  accumulate_by(~ID)

p <- ggplot(bf,aes(ID, Hours_watched, frame = frame)) +
  geom_line()

fig <- ggplotly(p, height = 400) %>%
  layout(
    title = "Hours watched",
    yaxis = list(
      title = "Total ammount",
      zeroline = F,
      tickprefix = "$"
    ),
    xaxis = list(
      title = "Month",
      zeroline = F, 
      showgrid = F
    )
  ) %>% 
  animation_opts(
    frame = 50, 
    transition = 0, 
    redraw = FALSE
  ) %>%
  animation_slider(
    currentvalue = list(
      prefix = "Month "
    )
  )

fig
```

