## EDA for Twitch data-set

These data comes from the website : [Twitchtracker](https://twitchtracker.com/statistics)

```{r, echo=FALSE, warning=FALSE, message=FALSE}
source(here::here("scripts/setup.R"))
```

```{r}
data1 <- read_delim(file = here::here("data/Twitch.csv"), ";", 
                    escape_double = FALSE, col_names = FALSE, trim_ws = TRUE)
```

Let's first load the dataset :

```{r}
# Data cleaning

TwitchData <- data1 %>%
  # set a name for each variable
  rename(Date = X1, Avg_concur_viewers = X2, 
         Avg_concur_channels = X3, Hours_watched = X4, 
         Active_streamers = X5, Hours_streamed = X6) %>%
  # modify the format of certain variable
  mutate(Date = mdy(Date), 
         Hours_watched = parse_number(Hours_watched)) %>%
  # Replace value with NA (in our dataframe, n/a are considered as character)
  replace_with_na(replace = list(Active_streamers = "n/a")) %>%
  mutate(Viewers_per_streamer = Hours_watched*1000000/Hours_streamed) %>%
  # Convert the column from character to double
  mutate(Active_streamers = parse_number(Active_streamers))

# Data overview

TwitchData %>% 
   kbl(caption = "Twitch statistics") %>%  
   kable_paper(full_width = F) %>% 
   scroll_box(width = "100%", height = "300px")

# test 
freq.na(TwitchData)
```
<p>&nbsp;</p>
We can see that these data consist of 99 observations of 7 attributes. 

## Here is a description of each attribute :
   
- `Date` : month in which the data apply
- `Avg_concur_viewers` : Number of viewers connected in the same time in average 
- `Avg_concur_channels` : Number of channels connected in the same time in average 
- `Hours_watched` (in million) : Total number of hours watched per month
- `Active_streamers` : Total number of active channels
- `Hours_streamed` : Total number of hours streamed per month
- `Viewers_per_streamer` : Average number of viewers per streamer per month


## Here the graph for each variable :

##### Average concurent viewers for each month :

```{r}
o_Avg_concur_viewers <- TwitchData %>%
    ggplot(aes(x = Date, y = Avg_concur_viewers)) +
    geom_col() +
    ylab("Average concurent viewers")

ggplotly(o_Avg_concur_viewers, height = 400)
```

##### Average concurent channels for each month:

```{r}
o_Avg_concur_channels <- TwitchData %>% 
    ggplot(aes(x = Date, y = Avg_concur_channels)) +
    geom_col() +
    ylab("Average concurent channels")

ggplotly(o_Avg_concur_channels, height = 400)

```

##### Total number of hours watched per month :

```{r}
o_Hours_watched <- TwitchData %>% 
    ggplot(aes(x = Date, y = Hours_watched)) +
    geom_col() +
    ylab("Hours watched")

ggplotly(o_Hours_watched, height = 400)

```

##### Total number of active channels

```{r}
o_Active_streamers <- TwitchData %>% 
  ggplot(aes(x = Date, y = Active_streamers)) +
  geom_col()+
  ylab("Average streamers")

ggplotly(o_Active_streamers, height = 400)
```

##### Total number of hours streamed per month

```{r}
o_Hours_streamed <- TwitchData %>% 
  ggplot(aes(x = Date, y = Hours_streamed)) +
  geom_col()+
  ylab("Hours streamed")

ggplotly(o_Hours_streamed, height = 400)

```

##### Average number of viewers per streamer per month

```{r}
o_Viewers_per_streamer <- TwitchData %>% 
  ggplot(aes(x = Date, y = Viewers_per_streamer)) +
  geom_col()+
  ylab("Viewers per streaner")

ggplotly(o_Viewers_per_streamer, height = 400)
```



