## EDA for Twitch data-set

These data comes from the website : [Twitchtracker](https://twitchtracker.com/statistics)

```{r, echo=FALSE, warning=FALSE, message=FALSE}
source(here::here("scripts/setup.R"))
```

Let's first load the dataset :

```{r}
data1 <- read_delim(file = here::here("data/Twitch.csv"), ";", escape_double = FALSE, col_names = FALSE, trim_ws = TRUE)

data1 %>% 
   kbl(caption = "Twitch statistics") %>%  
   kable_paper(full_width = F) %>% 
   scroll_box(width = "100%", height = "300px")
```
<p>&nbsp;</p>
As we can see, the dataset is not ready to be processed, we first need to clean it.

```{r}
TwitchData <- data1 %>%
  # set a name for each variable
  rename(Date = X1, Avg_concur_viewers = X2, 
         Avg_concur_channels = X3, Hours_watched = X4, 
         Active_streamers = X5, Hours_streamed = X6) %>%
  # modify the format of certain variable
  mutate(Date = mdy(Date), 
         Hours_watched = parse_number(Hours_watched)) %>%
  # Replace value with NA (in our dataframe, n/a are considered as character)
  replace_with_na(replace = list(Active_streamers = "n/a")) %>%
  mutate(Viewers_per_streamer = Hours_watched*1000000/Hours_streamed) %>%
  # Convert the column from character to double
  mutate(Active_streamers = parse_number(Active_streamers))

TwitchData %>% 
   kbl(caption = "Twitch statistics") %>%  
   kable_paper(full_width = F) %>% 
   scroll_box(width = "100%", height = "300px")
```
<p>&nbsp;</p>
The data are now clean and we can create some plot that will show useful information. 
We can see that these data consist of 99 observations of 7 attributes.

Here is a description of each attribute :
   
- `Date` : month in which the data apply
- `Avg_concur_viewers` : Number of viewers connected in the same time in average 
- `Avg_concur_channels` : Number of channels connected in the same time in average 
- `Hours_watched` (in million) : Total number of hours watched per month
- `Active_streamers` (grams) : Total number of active channels
- `Hours_streamed` : Total number of hours streamed per month
- `Viewers_per_streamer` : Average number of viewers per streamer per month


Here the graph for each variable 

```{r}
o_Avg_concur_viewers <- TwitchData %>% 
    ggplot(aes(x = Date, y = Avg_concur_viewers)) +
    geom_col() +
    ylab("Average concurent viewers")
o_Avg_concur_viewers

o_Avg_concur_channels <- TwitchData %>% 
    ggplot(aes(x = Date, y = Avg_concur_channels)) +
    geom_col() +
    ylab("Average concurent channels")

o_Avg_concur_channels

o_Hours_watched <- TwitchData %>% 
    ggplot(aes(x = Date, y = Hours_watched)) +
    geom_col() +
    ylab("Average concurent viewers")
o_Hours_watched

o_Active_streamers <- TwitchData %>% 
  ggplot(aes(x = Date, y = Active_streamers)) +
  geom_col()
o_Active_streamers

o_Hours_streamed <- TwitchData %>% 
  ggplot(aes(x = Date, y = Hours_streamed)) +
  geom_col()
o_Hours_streamed

o_Viewers_per_streamer <- TwitchData %>% 
  ggplot(aes(x = Date, y = Viewers_per_streamer)) +
  geom_col()
o_Viewers_per_streamer
```

```{r}
data2 <- read_delim(file = here::here("data/NZ_CompaniesPublicRevenues2.csv"), ";", escape_double = FALSE,
                    col_names = FALSE, trim_ws = TRUE)

CompaniesPublicRevenues <- data2 %>%
  rename(Company_name = X1, Region_of_HQ = X2, Q1_2019 = X3, Q2_2019 = X4, Q3_2019 = X5, Q4_2019 = X6, Q1_2020 = X7, Q2_2020 = X8) %>%
  mutate(Q1_2019 = parse_number(Q1_2019), Q2_2019 = parse_number(Q2_2019), 
         Q3_2019 = parse_number(Q3_2019), Q4_2019 = parse_number(Q4_2019), 
         Q1_2020 = parse_number(Q1_2020), Q2_2020 = parse_number(Q2_2020)) %>%
  mutate(Q1_2019 = ifelse(Q1_2019 < 10 , Q1_2019*1000, Q1_2019), 
         Q2_2019 = ifelse(Q2_2019 < 10 , Q2_2019*1000, Q2_2019), 
         Q3_2019 = ifelse(Q3_2019 < 10 , Q3_2019*1000, Q3_2019), 
         Q4_2019 = ifelse(Q4_2019 < 10 , Q4_2019*1000, Q4_2019),
         Q1_2020 = ifelse(Q1_2020 < 10 , Q1_2020*1000, Q1_2020),
         Q2_2020 = ifelse(Q2_2020 < 10 , Q2_2020*1000, Q2_2020)) %>%
  mutate(First_semester_of_2019 = Q1_2019 + Q2_2020, 
         Second_semester_of_2019 = Q3_2019 + Q4_2019, 
         Total_in_2019 = Q1_2019 + Q2_2019 + Q3_2019 + Q4_2019, 
         First_semester_in_2020 = Q1_2020 + Q2_2020) %>%
  mutate(Q1_grate = 100*(Q1_2020 - Q1_2019)/Q1_2019, 
         Q2_grate = 100*(Q2_2020 - Q2_2019)/Q2_2019, 
         Semester2_grate = 100*(Second_semester_of_2019 - First_semester_of_2019)/First_semester_of_2019,
         Semester3_grate = 100*(First_semester_in_2020 - Second_semester_of_2019)/Second_semester_of_2019,
         First_semester_grate = 100*(First_semester_in_2020 - First_semester_of_2019)/First_semester_of_2019)

kbl(CompaniesPublicRevenues) %>%
  kable_classic() %>%
  add_header_above(c(" " = 2, "2019" = 4, "2020" = 2, "Other" = 9))
```

```{r}
data3 <- read_delim(file = here::here("data/NZ_CompaniesInvestmentscsv1.csv"), ";", escape_double = FALSE, col_names = FALSE, trim_ws = TRUE)

data4 <- read_delim(file = here::here("data/NZ_CompaniesInvestmentscsv2.csv"), ";", escape_double = FALSE, col_names = FALSE, trim_ws = TRUE)

CompaniesInvestments <- data3 %>% full_join(data4) %>%
  rename(Date = X1, "Investment type" = X2, Sectors = X3, Emptycolumn = X4, Investee = X5, Amount = X6) %>%
  separate(Date, into = c("Day", "Month", "Year")) %>%
  mutate(Emptycolumn = NULL, Sectors = str_replace_all(Sectors, ",.", ", "))


CompaniesInvestments %>% 
   kbl(caption = "Twitch statistics") %>%  
   kable_paper(full_width = F) %>% 
   scroll_box(width = "100%", height = "300px")
```